\textbf{NBA Party}

### 2017-05-06 poster/poster.tex
Added stargazer tables and adjusted sticker-note containing email addresses.

\block{Mathematical Model}{
  \[
    \texttt{meet spread} \sim \texttt{party} + \substack{\texttt{days since} \\ \texttt{last game}} + \substack{\texttt{time}\\ \texttt{difference}} + \substack{\texttt{distance} \\ \texttt{traveled}}
  \]
}

\begin{columns}     \column{0.4}     \block{Data Sources}{
    \paragraph{Betting house data and game outcomes}
    We obtained data from 
    \href{http://www.covers.com/sports/NBA/matchups?selectedDate=2011-1-01}{Covers.com}, 
    which records the outcome of each game alongside the line set by a betting house.

@@

    }
    \column{0.6}     
    \block{NBA model}{
      Here,
      % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu % Date and time: Sat, May 06, 2017 - 09:58:05 AM

@@

\begin{columns}   \column{0.4}
  \block{Player Specific Model}{
    Here
  }
  \column{0.6}
  \block{MLB Model}{
    Here
  } \end{columns}

\begin{columns}     \column{0.5}     \block{Profits on MLB Betting in 2016}     {         \begin{tikzfigure}             \includegraphics[width=0.4\textwidth]{figures/mlb_bets}         \end{tikzfigure}     }     \column{0.5}     \block{Description of the figure}{
      On the left, we plot profits as a function of time over the 2016 season. For each relevant
      game, we place a bet if our model instructs us of odds sufficiently different from what
      the betting house suggests. We account for the bookmaker's cut. In the early season,
      at its worst we are out of pocket \$750 dollars. By season end, we have recouped all of
      our initial investment plus an additional \$13.5k.
    }
    \note[         
      targetoffsetx=-8cm,          
      targetoffsety=-6.5cm,          
      width=0.5\linewidth         
    ]{e-mail: \texttt{santucci@stanford.edu}}   \end{columns}

@@

  \begin{tikzfigure}
    \includegraphics[width=0.3\textwidth]{figures/gh_commits}
  \end{tikzfigure}
  \begin{tikzfigure}     \includegraphics[width=0.7\textwidth]{figures/punch_card}    \end{tikzfigure}
}

>>>>

\block{Model}{
  \[
    \texttt{meet spread} \sim \texttt{party} + \substack{\texttt{days since} \\ \texttt{last game}} + \substack{\texttt{time}\\ \texttt{difference}} + \substack{\texttt{distance} \\ \texttt{traveled}}
  \]
  Our setup relies on a quasi-experiment: we look for instances where a team plays in a city
  with active nightlife, then plays a game in a different location the next day. Since next-day
  opponent is uncorrelated with exposure to treatment, we have identification in our variable of 
  interest.
}

\begin{columns}     \column{0.6}     \block{Data Sources}{
    \paragraph{Betting house data and game outcomes}
    We obtained data from 
    \href{http://www.covers.com/sports/NBA/matchups?selectedDate=2011-1-01}{Covers.com}, 
    which records the outcome of each game alongside the line set by a betting house.

@@

    }
    \column{0.4}     
    \block{NBA model}{
      % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu % Date and time: Sat, May 06, 2017 - 09:58:05 AM
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]  \\[-1.8ex] & outcome == "W" \\  \hline \\[-1.8ex]   party & $-$0.052$^{**}$ (0.022) \\    lag.chg.pos & 0.0001 (0.002) \\    travel.dist & $-$0.00002 (0.00004) \\    ew & $-$0.035 (0.047) \\    nhours.lgame & 0.001 (0.001) \\    I(hour(date)) & 0.006 (0.012) \\    travel.dist:ew & 0.00004 (0.00005) \\    Constant & $-$0.144 (0.348) \\   \textit{N} & 9,979 \\  Log Likelihood & $-$6,912.426 \\  Akaike Inf. Crit. & 13,840.850 \\  \hline  \hline \\[-1.8ex]  \textit{Notes:} & \multicolumn{1}{r}{$^{***}$Significant at the 1 percent level.} \\   & \multicolumn{1}{r}{$^{**}$Significant at the 5 percent level.} \\   & \multicolumn{1}{r}{$^{*}$Significant at the 10 percent level.} \\  \end{tabular}

@@

\begin{columns}   \column{0.4}
  \block{Player Specific Model}{

    \begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]  \\[-1.8ex] & demeaned.reb.per.min \\  \hline \\[-1.8ex]   party & $-$0.001$^{*}$ (0.0005) \\    lag.chg.pos & 0.00003 (0.0001) \\    travel.dist & 0.00000$^{**}$ (0.00000) \\    nhours.lgame & 0.00002 (0.00002) \\    Constant & $-$0.003$^{**}$ (0.002) \\   \textit{N} & 44,190 \\  R$^{2}$ & 0.0003 \\  Adjusted R$^{2}$ & 0.0003 \\  Residual Std. Error & 0.105 (df = 44185) \\  F Statistic & 3.857$^{***}$ (df = 4; 44185) \\  \hline  \hline \\[-1.8ex]  \textit{Notes:} & \multicolumn{1}{r}{$^{***}$Significant at the 1 percent level.} \\   & \multicolumn{1}{r}{$^{**}$Significant at the 5 percent level.} \\   & \multicolumn{1}{r}{$^{*}$Significant at the 10 percent level.} \\  \end{tabular}

  }
  \column{0.6}
  \block{MLB Model}{

    \begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]  \\[-1.8ex] & I(team.score \textgreater  opponent.score) \\  \hline \\[-1.8ex]   party & $-$0.034$^{*}$ (0.019) \\    odds & 2.602$^{***}$ (0.162) \\    I(team == location) & 0.028 (0.033) \\    ndays.lgame & 0.012 (0.019) \\    travel.dist & 0.00000 (0.00003) \\    weekend & 0.042 (0.036) \\    Constant & $-$1.333$^{***}$ (0.080) \\   \textit{N} & 25,215 \\  Log Likelihood & $-$17,274.460 \\  Akaike Inf. Crit. & 34,562.920 \\  \hline  \hline \\[-1.8ex]  \textit{Notes:} & \multicolumn{1}{r}{$^{***}$Significant at the 1 percent level.} \\   & \multicolumn{1}{r}{$^{**}$Significant at the 5 percent level.} \\   & \multicolumn{1}{r}{$^{*}$Significant at the 10 percent level.} \\  \end{tabular}

\begin{columns}     \column{0.5}     \block{Profits on MLB Betting in 2016}     {         \begin{tikzfigure}             \includegraphics[width=0.4\textwidth]{figures/mlb_bets}         \end{tikzfigure}     }     \column{0.5}     \block{Description of the figure}{
      On the left, we plot profits as a function of time over the 2016 season. For each relevant
      game, we place a bet if our model instructs us of odds sufficiently different from what
      the betting house suggests. We account for the bookmaker's cut. In the early season,
      at its worst we are out of pocket \$750 dollars. By season end, we have recouped all of
      our initial investment plus an additional \$13.5k.
    }

@@

  \begin{tikzfigure}
    \includegraphics[width=0.6\linewidth]{figures/gh_commits}
  \end{tikzfigure}
}
\note[         
  targetoffsetx=-8cm,          
  targetoffsety=-8.5cm,          
  width=0.5\linewidth         
]{\texttt{elax13@stanford.edu}, \, \hspace{3pt} \texttt{santucci@stanford.edu}}

\end{columns}
